Survival Set Connectivity

### 2015-05-06 draft.tex
added RoundedGKR draft

We analyze the following problem, which we call Survival Set Connectivity (SSC): 
\begin{quote}
\textbf{Input}: A graph weighted $G = (V, E)$, $c: E \rightarrow \mathbb{R}$ and a collection of sets $(S_i, T_i)$, along with a value $k$. \\
\textbf{Output}: A minimum cost subgraph $H \subset G$ such that there are $k$ edge-disjoint paths between $S_i$ and $T_i$ for each $i$. 
\end{quote}

@@

\begin{definition}
A tree embedding of a weighted graph $G = (V, E)$ will be a tree $T = (V_T, E_T)$ with weights $y: E \rightarrow \mathbb{R}$ and a function $\text{map} : V_T \cup E_t \rightarrow V \cup P(E)$ ($P(E)$ is the power set of $E$) such that
\begin{align}
\text{map}(V_t) &\subset V \\
\text{map}(E_t) &\subset E
\end{align}
In other words, vertices map to vertices and edges map to edges. We will usually refer to an embedding as $(T, y, \text{map})$. 
\end{definition}

@@

\begin{definition}
Given a Racke tree, the load on an edge of the graph $e \in E$ is
\begin{align}
load(e) &= \sum_{f \in \text{map}^{-1}} y_f
\end{align}
The relative load, $rload(e) = \dfrac{load(e)}{x_e}$. 
\end{definition}

@@

\begin{lemma}
If we have a graph $G = (V, E)$ and capacities $x: E \rightarrow \mathbb{R}$ and a Racke tree $(T, y, \text{map})$. A multicommodity flow on $G$, $\{ f_i \}$, maps directly to a multicommodity flow on the tree which is also feasible. Likewise, a multicommodity flow on $T$ maps directly into a multicommodity flow on the graph, with the small caveat that we must multiply the capacity of the edge by the relative load. 
\end{lemma}

[ EXPLAIN HOW TO MAP FLOWS ]

\begin{lemma}
For some given graph $G = (V, E)$ and capacities $x: E \rightarrow \mathbb{R}$, we can sample efficiently from Racke trees of $G$, such that 
\begin{align}
\max_{e \in E} \textbf{E}[rload(e)] &\leq \alpha = O(\log n) 
\end{align}
\end{lemma}

\begin{lemma}
The height of the trees sampled is $O(\log nC)$, where $C$ is the ratio of the largest to smallest capacity in $G$. In our cases, the height will always be $O(\log n)$. 
\end{lemma}

@@

>>>>

We analyze the following problem, which we call Survival Set Connectivity (SSC): 
\begin{quote}
\textbf{Input}: A graph weighted $G = (V, E)$, $c: E \rightarrow \mathbb{R}^{\geq 0}$ and a collection of sets $(S_i, T_i)$, along with a value $k$. \\
\textbf{Output}: A minimum cost subgraph $H \subset G$ such that there are $k$ edge-disjoint paths between $S_i$ and $T_i$ for each $i$. 
\end{quote}

@@

\begin{definition}
A tree embedding of a weighted graph $G = (V, E)$ will be a tree $T = (V_T, E_T)$ with weights $y: E \rightarrow \mathbb{R}^{\geq 0}$ and a function $\text{map} : V_T \cup E_t \rightarrow V \cup P(E)$ ($P(E)$ is the power set of $E$) such that
\begin{align}
\text{map}(V_t) &\subset V \\
\text{map}(E_t) &\subset E
\end{align}
In other words, vertices map to vertices and edges map to edges. We will usually refer to an embedding as $(T, y, \text{map})$. 
\end{definition}

@@

\begin{definition}
Given a Racke tree, the load on an edge of the graph $e \in E$ is
\begin{align}
load(e) &= \sum_{f \in \text{map}^{-1}(e)} y_f
\end{align}
The relative load, $rload(e) = \dfrac{load(e)}{x_e}$. 
\end{definition}

@@

\begin{lemma}
\label{lem:mapflows}
If we have a graph $G = (V, E)$ and capacities $x: E \rightarrow \mathbb{R}^{\geq 0}$ and a Racke tree $(T, y, \text{map})$. A multicommodity flow on $G$, $\{ f_i \}$, maps directly to a multicommodity flow on the tree which is also feasible. Likewise, a multicommodity flow on $T$ maps directly into a multicommodity flow on the graph, with the small caveat that we must multiply the capacity of the edge by the relative load. 
\end{lemma}

\begin{lemma}
\label{lem:rload}
For some given graph $G = (V, E)$ and capacities $x: E \rightarrow \mathbb{R}^{\geq 0}$, we can sample efficiently from Racke trees of $G$, such that 
\begin{align}
\max_{e \in E} \textbf{E}[rload(e)] &\leq \alpha = O(\log n) 
\end{align}
\end{lemma}

\begin{lemma}
\label{thm:height}
The height of the trees sampled is $O(\log nC)$, where $C$ is the ratio of the largest to smallest capacity in $G$. In our cases, the height will always be $O(\log n)$. 
\end{lemma}

@@

The RoundGKR algorithm is an algorithm to rounding algorithm used for the Group Steiner Tree problem. We first describe the problem and give the algorithm. \\

Group Steiner Tree:
\begin{quote}
\textbf{Input}: A rooted tree $T = (V_t, E_t)$ at $r$ with costs $c: E_t \rightarrow \mathbb{R}^{\geq 0}$ as well as subsets of vertices $\{ T_i \}$. \\
\textbf{Output}: A minimum cost subtree $H \subset T$ with a path from $r$ to $t_i$ for some $t \in T_i$ for all $i$.
\end{quote}

A similar linear program produces a fractional solution, and the algorith RoundGKR is a way of rounding the solution back. The optimum to the linear program will be a set of values for each edge $y_e \in [0, 1]$. Since we are in a tree setting and we are looking for paths from the root, we can assume that $y_{p(e)} \geq y_e$ (parent edges are always greater).

The RoundGKR is simple, it starts at the root and makes its way down the tree as its being built. It includes the edge $e$ in the subtree with probability $\frac{y_e}{y_{p(e)}}$. A simple inductive argment shows that an edge $e$ is chosen with probability $y_e$. This is because $Pr[\text{include $e$}] = Pr[\text{include $e$ $|$ include $p(e)$}]*Pr[\text{include $p(e)$}] = y_e$ (if we don't include $p(e)$, then we don't include $e$.

The important property of the algorithm can be summarized in the following lemma, whose proof we refer to [CITE].

\begin{lemma}
\label{lem:findpath}
Suppose that $T = (V_t, E_t)$ support a flow of at least $1$ from $T_i$ to the root $r$ without the edges $F_t$. Then the RoundGKR returns a solution with a path in $T$ from $T_i$ to $r$ without using $F_t$ with probability at least $\Omega(\frac{1}{\log n})$. 
\end{lemma}

We will rely on this lemma heavily. In fact, since we need $\Omega(\frac{k}{\log n})$ edge-disjoint paths, we will argue that if we let $F_t$ be any set of at most $\Omega(\frac{k}{\log n})$ edges, then we still have a path, and therefore, we have $\Omega(\frac{k}{\log n})$ paths.
